### 2020-08-05 introduction.tex
ok

We can say that a static analysis tool kills a mutant when the \emph{number of warnings or errors}, which we call \emph{findings}, \emph{increases with mutation}.  In order to make this definition useful, we ignore informational or optimization related warnings (e.g., if a mutant is merely \emph{stylistically} suboptimal this is not ``finding a fault''). That is, a mutant is killed when a tool ``finds more bugs'' for the mutated code than for the un-mutated code.  This difference may be most easily interpreted when the original code produces no findings; we call such code \emph{clean}. For non-clean code, a tool conceivably could detect the mutant, but only change a previously generated finding, not add an additional finding.  However, even for non-clean code, \emph{most detected mutants should produce a new warning}.  We count findings, rather than consider their location or type, because some mutants cause a fault at a far-removed location.  Forcing tools to produce an \emph{additonal} warning is a conservative and automatable estimate of mutant detection.

@@

\section{Differential Mutation Analysis}

>>>>

We can say that a static analysis tool kills a mutant when the \emph{number of warnings or errors}, which we call \emph{findings}, \emph{increases with mutation}.  In order to make this definition useful, we ignore informational or optimization related warnings (e.g., if a mutant is merely \emph{stylistically} suboptimal this is not ``finding a fault''). That is, a mutant is killed when a tool ``finds more bugs'' for the mutated code than for the un-mutated code.  This difference may be most easily interpreted when the original code produces no findings; we call such code \emph{clean} (by analogy with Chekam et al.'s notion \cite{CleanProgram}). For non-clean code, a tool conceivably could detect the mutant, but only change a previously generated finding, not add an additional finding.  However, even for non-clean code, \emph{most detected mutants should produce a new warning}.  We count findings, rather than consider their location or type, because some mutants cause a fault at a far-removed location.  Forcing tools to produce an \emph{additonal} warning is a conservative and automatable estimate of mutant detection.

@@

 \section{Differential Mutation Analysis}
 \label{sec:method}
